---
title: "Group Assignment"
author: "Frixos Larkos"
date: "09/10/2019"
output: html_document
---

```{r huxtable-stuff, include=FALSE}
options("huxtable.knit_print_df" = FALSE)
library(lubridate)
library(here)
library(moderndive)
library(tidyverse)
library(ggfortify)
library(infer)
library(mosaic)
library(huxtable)
library(kableExtra)
library(tidyquant)
library(readxl) #need to load readxl explicitly, as it is not a core tidyverse 
library(GGally)
library(broom)
library(scales)
```

# Explanatory Data Analysis (EDA)

```{r load_data}

raw_data <- read_csv(here::here('Data', 'listings.csv.gz'))

```


## Looking at raw values

```{r EDA}

glimpse(raw_data)

```

## Looking at summary statistics

```{r summary_stats}

mosaic::favstats(price ~ city, data = raw_data)

skimr::skim(raw_data)

```

## Cleaning Data

```{r}

clean_data <- raw_data %>% 
  filter()

```

## Regressions

```{r correlation}

raw_data %>%
  

```


**Answer at minimum**: 
*1. How many variables/columns? How many rows/observations?* 

There are 106 variables and 19833 observations

*2. Which variables are numbers?*

(skim table - numeric)

3. Which are categorical or factor variables (numeric or character variables with variables that have a fixed and known set of possible values?

?

4. What are the correlations between variables? 


5. Does each scatterplot support a linear relationship between variables? 
6. Do any of the correlations appear to be conditional on the value of a categorical variable?

## Creating visualisations

```{r visualizations}

raw_data %>%
  #mutate(host_is_superhost = case_when(
    #host_is_superhost %in% TRUE ~ superhost, FALSE ~ non_superhost, NA)) %>%
  select(host_is_superhost, price, review_scores_rating) %>%
  na.omit() %>%
  ggpairs(aes(colour=host_is_superhost, alpha = 0.3))+
  theme_bw() 

```


## MAP (Noel)

```{r MAP}



raw_data_new <- raw_data %>%
  select(price, review_scores_rating) %>%
  filter(city == "Barcelona") %>%
    na.omit() 
    
raw_data_new %>%
  GGally::ggpairs()+
  theme_bw()



```

